Transferability of clinical prediction models for early trauma care

### 2019-06-02 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

---
title: "Mistriage"
author: "Martin Henriksson"
date: "190429"
output: word_document
---

@@

Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide (1, 2). Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase (3).

In a typical, high resource setting, the initial management of patients is performed on the scene of the trauma by Emergency Medical Services (EMS). Patient data, vital signs and scene information is transferred to the receiving hospital. This information is evaluated using a system to determine the level of trauma and prepare adequate resources (4), dictating if a full or limited trauma team is activated (5).

>>>>

---
title: "Transferability of clinical prediction models for early trauma care"
author: "Martin Henriksson"
date: "190602"
output: html_document
bibliography: library.bib
csl: bmcemerg.csl
---

@@

Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide [@RN1; @RN21]. Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase [@RN42].

In a typical, high resource setting, the initial management of patients is performed on the scene of the trauma by Emergency Medical Services (EMS). Patient data, vital signs and scene information is transferred to the receiving hospital. This information is evaluated using a system to determine the level of trauma and prepare adequate resources [@RN43], dictating if a full or limited trauma team is activated [@RN44].
